---
title: "Conversions Rabbit Hole"
output:
  html_document:
    df_print: paged
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  fig.width=12, 
  fig.height=8, 
  fig.path='Figs/',
  echo=FALSE,
  warning=FALSE,
  message=FALSE
  )
```

```{r setup}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(calibrate)
library(knitr)
basedir = "../../fromserver/results/rawdata/small/"
from_basedir = function(folder) {
  read_csv(paste(basedir, folder, sep=""))
}
results_summary <- from_basedir("conversion/results.callsite.summary.csv")
in_main = from_basedir("conversion/in-main/results.callsite.summary.csv")
in_test = from_basedir("conversion/in-test/results.callsite.summary.csv")
``` 

# Exploration of conversions

## Overall graph

The overall distribution of conversions, by location and by transitivity

```{r}
transform = function(df, where) {
  df %>%
    group_by(project, transitive) %>%
    summarise(count = sum(occurrences))
}

draw_transitivity_distribution = function(df, where) {
  ggplot(transform(df), aes(x = project, y = count, fill = transitive)) +
    geom_bar(stat = "identity", position = "dodge") +
    coord_flip() +
    theme(legend.position="bottom", legend.direction="horizontal",
                     legend.title = element_blank()) +
    labs(y = "# Conversions", x = "Project") +
    ggtitle(paste("Conversion transitivity distribution in", where)) +
    scale_fill_discrete(breaks=c("TRUE", "FALSE"),
                        labels=c("Transitive", "Non-transitive"))
}

draw_transitivity_distribution(results_summary, "ALL")
draw_transitivity_distribution(in_main, "Main")
draw_transitivity_distribution(in_test, "Test")
```


## Helper functions

We define the filters that we found for call sites:

```{r}
known_testing_framework = function(name) {
  grepl("^utest", name) |
  grepl("^org.scalatest", name) |
  grepl("^org.specs2", name)
}

arrow_assoc = function(name) {
  name == "scala.Predef.ArrowAssoc"
}

other_scala_predefs = function(name) {
  (grepl("^scala.Predef", name) & !arrow_assoc(name))
}

low_prio_implicits = function(name) {
  grepl("scala.LowPriorityImplicits", name)
}

contains_quote = function(name) {
  grepl("[qQ]uote", name)
}

scala_option = function(name) {
  grepl("^scala.Option", name)
}

other_options = function(name) {
  !scala_option(name) &
  grepl("Option", name)
}

other_scala = function(name) {
  !arrow_assoc(name) &
  !other_scala_predefs(name) &
  !scala_option(name) &
  grepl("^scala.", name)
}

akka_actor = function(name) {
  grepl("^akka.actor.actorRef2Scala", name) |
  grepl("^akka.actor.scala2ActorRef", name)
}
```

And some helper traversal functions:

```{r}

filter_name = function(df, f) {
  df[f(df$name),]
}

filter_occurrences = function(df, f) {
  df[f(df$occurrences),]
}

sum_ocurrences = function(df) {
  sum(df$occurrences)
}

remainder = function(data, filters) {
   data[Reduce("&", Map({function(fun) !fun(data$name)}, filters)), ]
}

printgraph = function(data, names, title) {
  data = as.integer(data)
  pct <- round(data/sum(data)*100)
  #names = paste(names, ": ", sep="")
  #names = paste(names, data)
  names = paste(names, "(")
  names = paste(names, pct) # add percents to labels
  names = paste(names,"%)",sep="") # ad % to labels
  f = data.frame(
    name = names,
    data = data
  )
  ggplot(f, aes(name, data)) +
    geom_bar(stat="identity") +
    coord_flip()
}
```

## All conversions per use

Modify the dataset to count conversions:

```{r}
all_conversions = results_summary %>%
  group_by(name) %>%
  summarise(occurrences = sum(occurrences)) %>%
  arrange(-occurrences)
```

Output the graph

```{r}
draw_conversion_distribution = function (df, title = "Distribution of transitive conversions by use ") {
  filters = c(known_testing_framework, arrow_assoc, other_scala_predefs, low_prio_implicits, contains_quote, scala_option, other_options, other_scala, akka_actor)
  total = sum_ocurrences(df)
  pietitle = paste(title, total)
  names = c("Unknown", "Testing libraries", "ArrowAssoc", "scala.Predef", "scala.LowPriorityImplicits", "Quotes", "Scala Options", "Other Options", "Other scala", "Akka actor <-> scala")

  distribution = Map({function(fun) sum_ocurrences(filter_name(df, fun))}, filters)

  with_totals = c(
    sum_ocurrences(remainder(df, filters)),
    distribution
  )

  printgraph(with_totals, names, pietitle)
}

draw_conversion_distribution(all_conversions, "Distribution of all conversions by use ")
```


## Exploration of transitive conversions

First we filter the dataset

```{r}
count_transitive_occurrences = function(df) {
  df[df$transitive,] %>%
    group_by(name) %>%
    summarise(occurrences = sum(occurrences)) %>%
    arrange(-occurrences)
}
transitive_conversions = count_transitive_occurrences(results_summary)
transitive_in_main = count_transitive_occurrences(in_main)
transitive_in_test = count_transitive_occurrences(in_test)
```


And finally, we can produce the graph

```{r}
draw_conversion_distribution(transitive_conversions)
draw_conversion_distribution(transitive_in_main, "Distribution of transitive conversions by use IN MAIN ")
draw_conversion_distribution(transitive_in_test, "Distribution of transitive conversions by use IN TEST ")
```

# Non-transitive conversions

Now let's plot the non-transitive conversion distribution. First, we filter out the transitive calls:

```{r}
nontransitive_conversions = results_summary[!results_summary$transitive,]
```

Then, we get the frequency counts, and we print it:

```{r}
summary = nontransitive_conversions %>%
  group_by(name) %>%
  summarise(occurrences = sum(occurrences)) %>%
  arrange(-occurrences)

freqCounts = nontransitive_conversions %>%
  group_by(occurrences) %>%
  summarise(count = n()) %>%
  arrange(occurrences, count)
plot(
  x = as.integer(freqCounts$count), 
  y = as.integer(freqCounts$occurrences), 
  log="yx", 
  xlab = "Number of implicits with that frequence",
  ylab= "Frequence: Number of conversions by this implicit", 
  main="Distribution of conversions by number of appearances"
)
```

This is not extremely useful, unfortunately.

We can envision another graph, with the same data but the axes changed:

```{r}
intervals = c(0, 1, 10, 100, 1000, 1000000)
partitioned = summary %>% 
  mutate(interval = cut(summary$occurrences, intervals, include.lowest=TRUE)) %>%
  group_by(interval) %>%
  summarise(num_in_interval = n())

ggplot(partitioned, aes(interval, num_in_interval)) +
  geom_bar(stat="identity")+
  coord_flip()
```


Now, if we _don't_ mush the projects together, maybe we can gather some metadata. First, load the project stats.

```{r}
project_metadata <- from_basedir("project-metadata.csv")
```

Then, add LOC information to the nontransitive conversions:

```{r}
locDistribution = 
  left_join(nontransitive_conversions, project_metadata, by=c("project" = "reponame")) %>%
  mutate(name = name.x) %>%
  group_by(project) %>%
  summarise(
    occurrences = sum(occurrences), 
    scala_loc = min(scala_loc),
    call_density = occurrences / scala_loc)

relevantNames = function(df) {
 Map({function(row) {if (row.call_density < 0.1) {row.project = ""}}}, df)
}

ggplot(locDistribution, aes(scala_loc, occurrences)) +
  geom_point() +
  geom_smooth() +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle("Distribution of non-transitive implicit conversions by scala LOC")
```

## Types HOF

```{r}
hof_size = 10

draw_HOF = function (hof, title) {
  ggplot(hof, aes(x = reorder(name, occurrences), y = occurrences, fill = what)) +
    geom_bar(stat="identity") +
    coord_flip() +
    facet_wrap(~what, scale="free_y") +
    theme(legend.position="bottom", legend.direction="horizontal",
                     legend.title = element_blank()) +
    #labs(y = "# Conversions", x = "Project") +
    scale_x_discrete(label=function(x) substring(x, nchar(x) - 40, nchar(x))) +
    #scale_y_continuous(breaks = unique(hof$occurrences)) +
    ggtitle(paste(title, "Hall of Fame"))
}

types_HOF = function(df, title) {
  count_by_name = function(df) {
    df %>% group_by(name) %>% summarise(occurrences = n()) %>% arrange(occurrences) %>% top_n(hof_size)
  }
  
  params_hof = df %>% mutate(name = param_type) %>% count_by_name %>% mutate(what = "param")
  returns_hof = df %>% mutate(name = return_type) %>% count_by_name %>% mutate(what = "return")
  
  data = rbind(params_hof, returns_hof)
  draw_HOF(data, title)
}
```


```{r}
get_all_hofs = function(header, conversions) {
  in_main = conversions[conversions$in_main, ]
  in_test = conversions[!conversions$in_main, ]
  ### Overall (Both test and main, both transitive and non-transitive)
  overall = types_HOF(conversions, 
                      paste(header, "Overall Conversion Type hall of fame"))
  ### Transitive
  #### In Main
  nont_conversions_in_main = types_HOF(in_main[in_main$transitive, ], 
                                       paste(header, "(NON-T in Main) Conversion"))
  #### In Test
  nont_conversions_in_test = types_HOF(in_test[in_test$transitive, ],
                                       paste(header, "(NON-T in Test) Conversion"))
  ### Non-Transitive
  #### In Main
  t_conversions_in_main = types_HOF(in_main[!in_main$transitive, ],
                                    paste(header, "(T in Main) Conversion Type"))
  #### In Test
  t_conversions_in_test = types_HOF(in_test[!in_test$transitive, ],
                                    paste(header, "(T in Test) Conversion Type"))
  
  grid.arrange(
    grobs = list(
      overall,
      nont_conversions_in_main,
      nont_conversions_in_test,
      t_conversions_in_test,
      t_conversions_in_main
    ),
    ncol = 1,
    nrow = 5
  )
}
load_by_path = function(base_subdir) {
  in_main = from_basedir(paste(base_subdir, "in-main/results.callsite.report.csv", sep="/")) %>% mutate(in_main = TRUE)
  in_test = from_basedir(paste(base_subdir, "in-test/results.callsite.report.csv", sep="/")) %>% mutate(in_main = FALSE)
  rbind(in_main, in_test)
}
```

## Halls of fame for all projects

```{r fig.height=20}
conversions = load_by_path("conversion")
get_all_hofs("[All Projects]", conversions)
```

## Halls of fame for Kamon

```{r fig.height=20}
#conversions = load_by_path("conversion") %>% filter(project == "kamon-io/Kamon")
#get_all_hofs("[Kamon]", conversions)
```

## Halls of fame for Better-files

```{r fig.height=20}
#conversions = load_by_path("conversion") %>% filter(project == "pathikrit/better-files")
#get_all_hofs("[Better-files]", conversions)
```

## Halls of fame for Json4s

```{r fig.height=20}
#conversions = load_by_path("conversion") %>% filter(project == "json4s/json4s")
#get_all_hofs("[Json4s]", conversions)
```

## Halls of fame for Quill

```{r fig.height=20}
#conversions = load_by_path("conversion") %>% filter(project == "getquill/quill")
#get_all_hofs("[Quill]", conversions)
```

# Identifying library primitives

## Non transitive conversions in main

```{r fig.height=40}
conversions = load_by_path("conversion") %>% 
  filter(in_main) %>% 
  filter(!transitive) %>%
  dplyr::select(project, param_type, return_type)

with_counts = unique(
    conversions %>%
    dplyr::select(param_type, project) %>%
    group_by(param_type) %>%
    mutate(occurrences = n()) %>%
    arrange(-occurrences)
  )

ggplot(with_counts, aes(x = reorder(param_type, occurrences), y = occurrences, fill = project)) +
  geom_bar(stat="identity") +
  coord_flip() +
  facet_grid(project ~ ., scale="free_y") +
  theme(legend.position="none") +
  scale_x_discrete(label=function(x) substring(x, nchar(x) - 50, nchar(x))) +
  #scale_y_continuous(breaks = unique(hof$occurrences)) +
  ggtitle("Most popular param types (Non transitive in main in Call Sites)")
```

Delving deeper into slick

```{r}
is_ast_base = function(name) {
  grepl("ast.", name)
}
slick_data = conversions %>% filter(project == "slick/slick") %>% filter(grepl("ast.", param_type))
with_counts = unique(
  slick_data %>% 
    mutate(signature = paste(param_type, return_type, sep = " => ")) %>%
    group_by(signature) %>% 
    mutate(occurrences = n())
  )
kable(with_counts %>% dplyr::select(signature, occurrences))
```
That was with call sites, let's go with 

## Definitions

```{r definitions-types, fig.height=100, }
definitions = from_basedir("conversion/results.definition.report.csv")
params = {
  with_counts = unique(
      definitions %>%
      dplyr::select(param_type, project) %>%
      group_by(param_type) %>%
      mutate(occurrences = n()) %>%
      arrange(-occurrences)
    )
  
  ggplot(with_counts, aes(x = reorder(param_type, occurrences), y = occurrences, fill = project)) +
    geom_bar(stat="identity") +
    coord_flip() +
    facet_grid(project ~ ., scale="free_y") +
    theme(legend.position="none") +
    scale_x_discrete(label=function(x) substring(x, nchar(x) - 30, nchar(x))) +
    #scale_y_continuous(breaks = unique(hof$occurrences)) +
    ggtitle("Most popular param types in definitions")
}
returns = {
  with_counts = unique(
      definitions %>%
      dplyr::select(return_type, project) %>%
      group_by(return_type) %>%
      mutate(occurrences = n()) %>%
      arrange(-occurrences)
    )
  
  ggplot(with_counts, aes(x = reorder(return_type, occurrences), y = occurrences, fill = project)) +
    geom_bar(stat="identity") +
    coord_flip() +
    facet_grid(project ~ ., scale="free_y") +
    theme(legend.position="none") +
    scale_x_discrete(label=function(x) substring(x, nchar(x) - 30, nchar(x))) +
    #scale_y_continuous(breaks = unique(hof$occurrences)) +
    ggtitle("Most popular return types in definitions")
}

grid.arrange(
  params,
  returns,
  ncol = 2
)
```










