---
title: "Overall project information"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  fig.width=12, 
  fig.height=8, 
  fig.path='Figs/',
  echo=FALSE,
  warning=FALSE,
  message=FALSE
  )
```

```{r setup}
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
basedir = "./rawdata/small/"
from_basedir = function(folder) {
  read_csv(paste(basedir, folder, sep=""))
}
project_data = from_basedir("project-metadata.csv")
sorted_by_sloc = project_data[order(project_data$scala_loc), ]
```

# Overall information about projects.

Some basic information about the LOC distribution in projects:

```{r}
barplot(
  sorted_by_sloc$scala_loc / 1000, 
  las = 2, cex.names = 0.2,
  names.arg = sorted_by_sloc$reponame, 
  horiz = TRUE,
  main = "Thousands of Scala LOC per project"
  )
```
```{r}
slocs = from_basedir("slocs.csv")
slocs = slocs %>%
  filter(grepl("Scala|Java|Javascript", language))

uprojs = unique(slocs$project)

scala = slocs %>% filter(language == "Scala") %>% select(project, code)
java = slocs %>% filter(language == "Java") %>% select(project, code)
js = slocs %>% filter(language == "Javascript") %>% select(project, code)

unwrapped = scala %>% 
  left_join(java, by="project") %>% 
  left_join(js, by="project") %>%
  mutate(scala_loc = code.x, java_loc = code.y, js_loc = code) %>%
  select(c("project", "scala_loc", "java_loc", "js_loc"))
unwrapped[is.na(unwrapped)] = 0

normalized = unwrapped %>%
  mutate(total = scala_loc + java_loc + js_loc) %>%
  mutate(scala_loc = scala_loc / total) %>%
  mutate(java_loc = java_loc / total) %>%
  mutate(js_loc = js_loc / total)

counts = t(as.matrix(normalized, replace=TRUE))
barplot(
  counts[2:4, ],
  horiz = TRUE,
  col = c("pink", "cyan", "purple"),
  legend = c("Scala", "Java", "JS"),
  main="Distribution of relevant languages in projects",
  las = 2, cex.names = 0.5,
  names.arg = counts[1,]
  )
```

Note that projects whose star count we couldn't get were omitted.

```{r}
# Sloc / gh stars
data = sorted_by_sloc[which(sorted_by_sloc$gh_stars != -1), ]
plot(
  x = data$gh_stars,
  y = data$scala_loc / 1000,
  log = "xy",
  main = "Thousands of Scala LOC per GH stars (log scale)",
  xlab = "GH stars of a project",
  ylab = "1000s of Scala LOC",
  sub = paste("cor: ", cor(data$gh_stars, data$scala_loc))
)
```

# Call distribution

```{r}
call_site_counts = from_basedir("callsite-counts.all.csv")  %>%
  mutate(both = insource + synthetic) %>%
  left_join(project_data, by=c("project"="name"))

by_project = call_site_counts %>%
  group_by(reponame) %>%
  summarise(insource = sum(insource), synthetic = sum(synthetic), both = sum(both)) %>%
  mutate(insource_percent = insource / both, 
         synthetic_percent = synthetic / both)

by_project_long = gather(by_project, where, percentage, insource_percent:synthetic_percent, factor_key=TRUE)

ggplot(by_project_long, aes(x = reponame, y = percentage, fill = where)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme(legend.position="bottom", legend.direction="horizontal",
                   legend.title = element_blank()) +
  labs(y = "Percentage of call sites", x = "Project") +
  ggtitle("Distribution of call sites between synthetic and in-source")
```


# Pattern appearance per project

- How many call sites with implicit parameters it has
- How many implicit conversions it has

```{r}
with_implicits = from_basedir("all/results.project.summary.csv")
conversions = from_basedir("conversion/results.project.summary.csv")
collection = by_project %>%
  left_join(with_implicits, by=c("reponame"="project")) %>%
  mutate(implicit_callsites = call_sites_after_filter) %>%
  dplyr::select(-call_sites_after_filter, -call_sites_before_filter) %>%
  left_join(conversions, by=c("reponame"="project")) %>%
  mutate(conversions = call_sites_after_filter) %>%
  dplyr::select(-call_sites_after_filter, -call_sites_before_filter) %>%
  mutate(without_conversion = implicit_callsites - conversions)

collection_long = gather(collection, what, callsites, c(insource, synthetic, implicit_callsites, conversions), factor_key=TRUE)

ggplot(collection_long, aes(reponame, callsites)) +
  geom_bar(aes(fill = what), position = "dodge", stat="identity") +
  coord_flip()
```


The main idea is to see at a glance which projects include which patterns in what form.


