---
title: "Conversions Rabbit Hole"
output:
  html_document:
    df_print: paged
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  fig.width=12, 
  fig.height=8, 
  fig.path='Figs/',
  echo=FALSE,
  warning=FALSE,
  message=FALSE
  )
```

```{r setup}
library(readr)
library(dplyr)
library(calibrate)
results_summary <- read_csv("~/work/scala/results/conversion/results.callsite.summary.csv") %>% 
  mutate(transitive = !transitive) # Should fix that in the impl
``` 

# Exploration of transitive conversions

First we filter the dataset

```{r}
count_transitive = function(df) {
  df[df$transitive,] %>%
    group_by(name) %>%
    summarise(occurrences = sum(occurrences)) %>%
    arrange(-occurrences)
}

transitive_conversions = count_transitive(results_summary)
transitive_in_main = count_transitive(in_main)
transitive_in_test = count_transitive(in_test)
```

Now we define the filters that we found for call sites:

```{r}

known_testing_framework = function(name) {
  grepl("^utest", name) |
  grepl("^org.scalatest", name) |
  grepl("^org.specs2", name)
}

arrow_assoc = function(name) {
  name == "scala.Predef.ArrowAssoc"
}

other_scala_predefs = function(name) {
  (grepl("^scala.Predef", name) & !arrow_assoc(name))
}

low_prio_implicits = function(name) {
  grepl("scala.LowPriorityImplicits", name)
}

contains_quote = function(name) {
  grepl("[qQ]uote", name)
}

scala_option = function(name) {
  grepl("^scala.Option", name)
}

other_options = function(name) {
  !scala_option(name) &
  grepl("Option", name)
}

other_scala = function(name) {
  !arrow_assoc(name) &
  !other_scala_predefs(name) &
  !scala_option(name) &
  grepl("^scala.", name)
}

akka_actor = function(name) {
  grepl("^akka.actor.actorRef2Scala", name) |
  grepl("^akka.actor.scala2ActorRef", name)
}
```

And some helper traversal functions:

```{r}

filter_name = function(df, f) {
  df[f(df$name),]
}

filter_occurrences = function(df, f) {
  df[f(df$occurrences),]
}

sum_ocurrences = function(df) {
  sum(df$occurrences)
}

remainder = function(data, filters) {
   data[Reduce("&", Map({function(fun) !fun(data$name)}, functions)), ]
}

printgraph = function(data, names, title) {
  data = as.integer(data)
  pct <- round(data/sum(data)*100)
  #names = paste(names, ": ", sep="")
  #names = paste(names, data)
  names = paste(names, "(")
  names = paste(names, pct) # add percents to labels
  names = paste(names,"%)",sep="") # ad % to labels
  barplot(data, names.arg = names, horiz = TRUE, main=title, cex.names = 0.6, las = 2)
}
```

And finally, we can produce the graph

```{r}
total = sumOccurrences(transitive_conversions)
pietitle = paste("Distribution of transitive conversions by use ", total)
names = c("Unknown", "Testing libraries", "ArrowAssoc", "scala.Predef", "scala.LowPriorityImplicits", "Quotes", "Scala Options", "Other Options", "Other scala", "Akka actor <-> scala")
functions = c(knownTestingFramework, arrowAssoc, otherScalaPredefs, lowPrioImplicits, containsQuote, scalaOption, otherOptions, otherScala, akkaActor)
distribution = Map({function(fun) sumOccurrences(filterName(transitive_conversions, fun))}, functions)

withTotals = c(
  sumOccurrences(remainder(transitive_conversions, functions)),
  distribution
)

printgraph(withTotals, names, pietitle)
```

# Non-transitive conversions

Now let's plot the non-transitive conversion distribution. First, we filter out the transitive calls:

```{r}
nontransitive_conversions = results_summary[!results_summary$transitive,]
```

Then, we get the frequency counts, and we print it:

```{r}
summary = nontransitive_conversions %>%
  group_by(name) %>%
  summarise(occurrences = sum(occurrences)) %>%
  arrange(-occurrences)

freq_counts = nontransitive_conversions %>%
  group_by(occurrences) %>%
  summarise(count = n()) %>%
  arrange(occurrences, count)
plot(
  x = as.integer(freq_counts$count),
  y = as.integer(freq_counts$occurrences),
  log="yx", 
  xlab = "Number of implicits with that frequence",
  ylab= "Frequence: Number of conversions by this implicit", 
  main="Distribution of conversions by number of appearances"
)
```

This is not extremely useful, unfortunately.

Now, if we _don't_ mush the projects together, maybe we can gather some metadata. First, load the project stats.

```{r}
project_metadata <- read_csv("~/work/scala/tmp/results/project-metadata.csv")
```

Then, add LOC information to the nontransitive conversions:

```{r}
loc_distribution =
  left_join(nontransitive_conversions, project_metadata, by=c("project" = "reponame")) %>%
  mutate(name = name.x) %>%
  group_by(project) %>%
  summarise(
    occurrences = sum(occurrences), 
    scala_loc = min(scala_loc),
    call_density = occurrences / scala_loc)

relevantNames = function(df) {
 Map({function(row) {if (row.call_density < 0.1) {row.project = ""}}}, df)
}

plot(
  x = as.integer(loc_distribution$scala_loc),
  y = as.integer(loc_distribution$occurrences),
  xlab = "Scala LOC", 
  ylab = "Non-transitive implicit conversions", 
  main="Distribution of non-transitive implicit conversions by scala LOC"
  )
textxy(
  loc_distribution$scala_loc,
  loc_distribution$occurrences,
  loc_distribution$project
  )
```
